Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-22 paper.tex
more formatting

        Dask array functions all create an \textit{Array} object which contains 
        the dask graph \textit{.dask}, details on the overall shape and the 
        shape of each subdivided portion (chunk) of the array (\textit{.chunks})
        , the \textit{.name} representing which keys map to the results, and the
        data type.

@@

        The Dask bag contains functions like \textit{map} and \textit{filter}, 
        in addition to many other functions that can be found in the PyToolz API
        . It is particularly well suited for the handling of data dumps.

        The Dask dataframe consists of a collection of Pandas DataFrames, and 
        thus implements many of the functionalities found in an Pandas DataFrame
        . The dataframe is well suited for running on partioned datasets, where 
        partitions are clearly defined by an index.

>>>>

            Dask array functions all create an \textit{Array} object which 
            contains the dask graph \textit{.dask}, details on the overall shape
            and the shape of each subdivided portion (chunk) of the array 
            (\textit{.chunks}), the \textit{.name} representing which keys map 
            to the results, and the data type.

@@

            The Dask bag contains functions like \textit{map} and 
            \textit{filter}, in addition to many other functions that can be 
            found in the PyToolz API. It is particularly well suited for the 
            handling of data dumps.

            The Dask dataframe consists of a collection of Pandas DataFrames, 
            and thus implements many of the functionalities found in an Pandas 
            DataFrame. The dataframe is well suited for running on partioned 
            datasets, where partitions are clearly defined by an index.
